---
title: "Unit 9 - 9.5 code"
author: "Alex Deshowitz"
date: "July 10, 2016"
output: html_document
---

* This markdown file will walk through downloading the data, calculating log returns, calculating volatility, and calculing it over the length of the data.  Additionally, this document will provide graphs of the volatility data with 3 different decay factors.

* First, we need to load the required packages

```{r library, echo = TRUE}

library(tseries)

```

* Download the data

```{r download SPX data, echo = TRUE}
spx_data<- get.hist.quote(instrument ="^gspc",quote = "Close")

```

* Create the log return with 1 period lag

```{r log return, echo = TRUE}

spx_return<- log(lag(spx_data))- log(spx_data)

```

* Create the volatiltiy parameter ( 250 trading days)

```{r volatility, echo = TRUE}

spx_volatility<- sd(spx_return)*sqrt(250)*100

spx_volatility

```

* We can see that the SPX volaitlity is .18

* Now, we input a function for the volatility

```{r volatility function, echo = TRUE}
vol<- function(d, logrets){
  var = 0
  lam = 0
  varlist<- c()
  for(r in logrets){
    lam = lam*(1-1/d)+1
  var = (1-1/lam)*var+(1/lam)*r^2
    varlist<- c(varlist,var)
  
  }
sqrt(varlist)
}

```

* Then we create three different volatility curve decay factors

```{r decay factors,  echo = TRUE}
volest<- vol(10,spx_return)
volest2<- vol(30,spx_return)
volest3<- vol(100, spx_return)

```


* finally, we plot the decay factors for the volatility

```{r plots, echo = TRUE}

plot(volest,type = "l")
lines(volest2, type = "l", col = "red")
lines(volest3, type = "l", col = "blue")

```
